Lessons Learned for JWST Transiting Planet Time Series from Ground-based Studies of the NIRCam Detectors

### 2019-07-31 ms.tex
added examples of time series with no backsub nor refpix to show a more dramatic change between RPI and RPF

\begin{figure*}
{\gridline{\fig{azlab_ratio_tser_baseline.pdf}{0.33\textwidth}{Reset-per-frame, 2048x256}
\fig{azlab_ratio_tser_RPI.pdf}{0.33\textwidth}{Reset-per-integration, 2048x256}}}
{\gridline{\fig{azlab_ratio_tser_stripe64_1p5_mA_rpt2.pdf}{0.33\textwidth}{Reset-per-frame, 2048x64}
\fig{azlab_ratio_tser_stripe64_1p5_mA_rpt3rpi.pdf}{0.33\textwidth}{Reset-per-integration, 2048x64}}}
\caption{Reset per integration versus reset per frame.}\label{fig:RPFvsRPItseries}
\end{figure*}

>>>>

\begin{figure*}
{\gridline{\fig{azlab_ratio_tser_rpi_vs_rpf_no_bsub_no_refpix_rpf256_no_bsub_no_refpx_both_NRCBSELINE0P9MA.pdf}{0.33\textwidth}{Reset-per-frame, 2048x256}
\fig{azlab_ratio_tser_rpi_vs_rpf_no_bsub_no_refpix_rpi256_no_bsub_no_refpx_both_NRCRPIBSELINE0P9MA.pdf}{0.33\textwidth}{Reset-per-integration, 2048x256}}}
{\gridline{\fig{azlab_ratio_tser_rpi_vs_rpf_no_bsub_no_refpix_rpf064_no_bsub_no_refpx_both_NRC64STRIPE1P5MA.pdf}{0.33\textwidth}{Reset-per-frame, 2048x64}
\fig{azlab_ratio_tser_rpi_vs_rpf_no_bsub_no_refpix_rpi064_no_bsub_no_refpx_both_NRCRPI64STRIPE1P5MA.pdf}{0.33\textwidth}{Reset-per-integration, 2048x64}}}
\caption{Reset per integration versus reset per frame where no reference pixel correction and no background subtraction have been applied.}\label{fig:RPFvsRPItseries}
\end{figure*}

\begin{figure*}
{\gridline{\fig{azlab_ratio_tser_baseline.pdf}{0.33\textwidth}{Reset-per-frame, 2048x256}
\fig{azlab_ratio_tser_RPI.pdf}{0.33\textwidth}{Reset-per-integration, 2048x256}}}
{\gridline{\fig{azlab_ratio_tser_stripe64_1p5_mA_rpt2.pdf}{0.33\textwidth}{Reset-per-frame, 2048x64}
\fig{azlab_ratio_tser_stripe64_1p5_mA_rpt3rpi.pdf}{0.33\textwidth}{Reset-per-integration, 2048x64}}}
\caption{Reset per integration versus reset per frame where both reference pixel correction and background subtraction have been applied.}\label{fig:RPFvsRPItseries}
\end{figure*}
